---
title: "SQANTISIM OUTPUT COMPARISON REPORT"
author: "`r paste0('  ','Author', ': ',Sys.getenv('USERNAME'))`"
date: "`r paste0('  ','Date', ': ', format(Sys.time(), '%d %B %Y'))`"
output:
  html_document:
    number_sections: false
    toc: true
    toc_float: true
    toc_depth: 3
    theme: spacelab
---

<!-- Basic setting -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, cache = FALSE, echo = FALSE)
```

<!-- Report generation -->

## Summary

```{r, results='asis'}
n.sim.trans <- nrow(res.full$data.known) +  nrow(res.full$data.novel)
n.known.trans <- nrow(res.full$data.known)
n.novel.trans <- nrow(res.full$data.novel)
n.class.trans <- nrow(data.query)

cat('\n\n**Number of simulated transcripts**: ', n.sim.trans, '\n\n')
cat('\n\n**Number of known transcripts**: ', n.known.trans, '\n\n')
cat('\n\n**Number of novel transcripts**: ', n.novel.trans, '\n\n')
cat('\n\n**Number of reconstructed transcripts**: ', n.class.trans, '\n\n')
```

## Simulated counts distribution

```{r}
p1
```

## Isoform classification distribution of reconstructed transcripts

```{r}
p2
```

## Evaluation of simulation 

Simulated transcript were grouped in know simulated transcripts which appear in the reference annotation GTF and novel simulated transcripts that were deleted from the annotation. The following metrics were computed:

- **Number of isoforms simulated**: Total number of simulated isoforms
- **True Positive isoforms (TP)**: Isoforms that match junctions with a simulated transcript and its TSS and TTS is within the 50bp threshold
- **Partial True Positive isoforms (PTP)**: Isoforms that match junctions but the TSS and TTS are beyond the threshold
- **False Negative isoforms (FN) **: Isoforms that were simulated but not detected
- **False Positive (FP)**: Transcript that were detected but not simulated
- **Sensitivity**: TP/Number of simulated transcripts
- **Precision**: TP/Detected isoforms
- **F-score**: Harmonic mean of precision and sensitivity
- **False Discovery Rate**: (FP+PTP)/Detected isoforms
- **Positive Detection Rate**: (TP + PTP)/Number of simulated transcripts
- **False Detection Rate**: FP/Detected isoforms

## Performance metrics {.tabset}

### Full results

```{r}
t1
```

```{r, results = 'hide'}
radar.palette <- c("Known"="#750037", "Novel"='#052240', "FSM"="#6BAED6", "ISM"="#FC8D59", "NIC"="#78C679", 
                "NNC"="#EE6A50", "Genic\nGenomic"="#969696", "Antisense"="#66C2A4", "Fusion"="goldenrod1",
                "Intergenic" = "darksalmon", "Genic\nIntron"="#41B6C4")
sqantisim.stats.t <- as.data.frame(t(as.matrix(res.full$sqantisim.stats)))
sqantisim.stats.t[is.na(sqantisim.stats.t)] <- NA
sqantisim.stats.t <-sqantisim.stats.t[,c("Sensitivity", "Precision", "F-score", "False_Discovery_Rate", "Positive_Detection_Rate", "False_Detection_Rate")]
sqantisim.stats.t <- rbind(1, 0, sqantisim.stats.t)

par(mar=c(1,1,1,1), mfrow=c(1,2))
for (i in 1:2){
  radarchart(
  sqantisim.stats.t[c(1, 2, i+2),], axistype = 1,
  pcol = radar.palette[[rownames(sqantisim.stats.t)[i+2]]], pfcol = scales::alpha(radar.palette[[rownames(sqantisim.stats.t)[i+2]]], 0.5), plwd = 2, plty = 1,
  # Customize the grid
  cglcol = "grey", cglty = 1, cglwd = 0.8,
  # Customize the axis
  axislabcol = "grey", 
  # Variable labels
  vlcex = 0.7, vlabels = colnames(sqantisim.stats.t[c(1, 2, i+2),]),
  caxislabels = c(0, 0.25, 0.5, 0.75, 1), title = rownames(sqantisim.stats.t)[i+2]
)
}

par(mar=c(1,1,1,1), mfrow=c(2,ceiling((nrow(sqantisim.stats.t)-4)/2)))
for (i in 3:(nrow(sqantisim.stats.t)-2)){
  radarchart(
  sqantisim.stats.t[c(1, 2, i+2),], axistype = 1,
  pcol = radar.palette[[rownames(sqantisim.stats.t)[i+2]]], pfcol = scales::alpha(radar.palette[[rownames(sqantisim.stats.t)[i+2]]], 0.5), plwd = 2, plty = 1,
  # Customize the grid
  cglcol = "grey", cglty = 1, cglwd = 0.8,
  # Customize the axis
  axislabcol = "grey", 
  # Variable labels
  vlcex = 0.7, vlabels = colnames(sqantisim.stats.t[c(1, 2, i+2),]),
  caxislabels = c(0, 0.25, 0.5, 0.75, 1), title = rownames(sqantisim.stats.t)[i+2]
)
}
```

#### Plots {.tabset}

##### Number of exons

```{r}
p3
```

##### Canonical Junctions

```{r}
p4
```

```{r, results='asis'}
if ('within_cage_peak' %in% colnames(data.index)){
  cat('\n\n##### CAGE Peak Support\n\n')
  print(p5)
  print(p6)
}

if ('min_cov' %in% colnames(data.index)){
  cat('\n\n##### Short Reads Support\n\n')
  print(p7)
  print(p8)
}
```

### Above min. supp. results

```{r}
t2
```

```{r, results = 'hide'}
radar.palette <- c("Known"="#750037", "Novel"='#052240', "FSM"="#6BAED6", "ISM"="#FC8D59", "NIC"="#78C679", 
                "NNC"="#EE6A50", "Genic\nGenomic"="#969696", "Antisense"="#66C2A4", "Fusion"="goldenrod1",
                "Intergenic" = "darksalmon", "Genic\nIntron"="#41B6C4")
sqantisim.stats.t <- as.data.frame(t(as.matrix(res.min$sqantisim.stats)))
sqantisim.stats.t[is.na(sqantisim.stats.t)] <- NA
sqantisim.stats.t <-sqantisim.stats.t[,c("Sensitivity", "Precision", "F-score", "False_Discovery_Rate", "Positive_Detection_Rate", "False_Detection_Rate")]
sqantisim.stats.t <- rbind(1, 0, sqantisim.stats.t)

par(mar=c(1,1,1,1), mfrow=c(1,2))
for (i in 1:2){
  radarchart(
  sqantisim.stats.t[c(1, 2, i+2),], axistype = 1,
  pcol = radar.palette[[rownames(sqantisim.stats.t)[i+2]]], pfcol = scales::alpha(radar.palette[[rownames(sqantisim.stats.t)[i+2]]], 0.5), plwd = 2, plty = 1,
  # Customize the grid
  cglcol = "grey", cglty = 1, cglwd = 0.8,
  # Customize the axis
  axislabcol = "grey", 
  # Variable labels
  vlcex = 0.7, vlabels = colnames(sqantisim.stats.t[c(1, 2, i+2),]),
  caxislabels = c(0, 0.25, 0.5, 0.75, 1), title = rownames(sqantisim.stats.t)[i+2]
)
}

par(mar=c(1,1,1,1), mfrow=c(2,ceiling((nrow(sqantisim.stats.t)-4)/2)))
for (i in 3:(nrow(sqantisim.stats.t)-2)){
  radarchart(
  sqantisim.stats.t[c(1, 2, i+2),], axistype = 1,
  pcol = radar.palette[[rownames(sqantisim.stats.t)[i+2]]], pfcol = scales::alpha(radar.palette[[rownames(sqantisim.stats.t)[i+2]]], 0.5), plwd = 2, plty = 1,
  # Customize the grid
  cglcol = "grey", cglty = 1, cglwd = 0.8,
  # Customize the axis
  axislabcol = "grey", 
  # Variable labels
  vlcex = 0.7, vlabels = colnames(sqantisim.stats.t[c(1, 2, i+2),]),
  caxislabels = c(0, 0.25, 0.5, 0.75, 1), title = rownames(sqantisim.stats.t)[i+2]
)
}
```

##### Number of exons

```{r}
p3.min
```

##### Canonical Junctions

```{r}
p4.min
```

```{r, results='asis'}
if ('within_cage_peak' %in% colnames(data.index)){
  cat('\n\n##### CAGE Peak Support\n\n')
  print(p5.min)
  print(p6.min)
}

if ('min_cov' %in% colnames(data.index)){
  cat('\n\n##### Short Reads Support\n\n')
  print(p7.min)
  print(p8.min)
}
```
